Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-21 paper/main.tex
cleanup

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={% TODO
},
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={Jonas Pleyer, Christian Fleck},
pdfkeywords={},
}

% Change numbering of equations
% \numberwithin{equation}{section}

% MAKE TITLES IN THEOREMS BOLD
\makeatletter
\def\th@plain{%
  \thm@notefont{}% same as heading font
  \itshape % body font
}
\def\th@definition{%
  \thm@notefont{}% same as heading font
  \normalfont % body font
}
\makeatother

@@

\begin{itemize}
    \item Adapt introduction; \acp{abm} not focus of paper, but rather tool to do the job
    \begin{itemize}
        \item model division, growth of bacteria
        \item \acp{abm} are good for this tool
    \end{itemize}
    \item Exchange $\sigma \rightarrow R_1+R_2$
    \item Equation 8 make double norm $||\vec{F}||$
    \item Remove auxiliary variable $\vec{F}$ only use $\vec{\nabla}V$
    \item Table 2 in supplement? (probably not)
    \item numerical implementation verschieben?
    \item numerical implementation: waht do we need to simulate this?
    \begin{itemize}
        \item \acp{abm} are common tools to realize this
        \item cellular\_raza is THE tool to do it
    \end{itemize}
    \item Methodology: single-cell parameter estimation as motivation for techniques
    \item Which parameters are global which are individual? Discuss this in general; not in detail
    \item depends on data, number of parameters (computational efficiency)
    \item page 12; yes this is Discussion
    \item page 12: maybe extend the paragraph wrt comparison in intervals
\end{itemize}

>>>>

@@

% \begin{itemize}
%     \item Adapt introduction; \acp{abm} not focus of paper, but rather tool to do the job
%     \begin{itemize}
%         \item model division, growth of bacteria
%         \item \acp{abm} are good for this tool
%     \end{itemize}
%     \item Exchange $\sigma \rightarrow R_1+R_2$
%     \item Equation 8 make double norm $||\vec{F}||$
%     \item Remove auxiliary variable $\vec{F}$ only use $\vec{\nabla}V$
%     \item Table 2 in supplement? (probably not)
%     \item numerical implementation verschieben?
%     \item numerical implementation: waht do we need to simulate this?
%     \begin{itemize}
%         \item \acp{abm} are common tools to realize this
%         \item cellular\_raza is THE tool to do it
%     \end{itemize}
%     \item Methodology: single-cell parameter estimation as motivation for techniques
%     \item Which parameters are global which are individual? Discuss this in general; not in detail
%     \item depends on data, number of parameters (computational efficiency)
%     \item page 12; yes this is Discussion
%     \item page 12: maybe extend the paragraph wrt comparison in intervals
% \end{itemize}
